They're Clutching up! Team Momentum in Round-Based Esports

### 2022-08-12 presentation.qmd
don't run code in the paper

cod_o_win_prop_const <- cod_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)
cod_o_win_pct <- scales::percent(cod_o_win_prop_const, accuracy = 1)

cod_plant_pct <- cod_rounds |>
  filter(is_offense) |> 
  count(makes_plant = !is.na(plant)) |> 
  mutate(prop = n / sum(n)) |> 
  filter(makes_plant) |> 
  pull(prop) |> 
  scales::percent(accuracy = 1)

cod_o_plant_and_win_pct <- cod_rounds |> 
  filter(is_offense, !is.na(plant)) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop) |> 
  scales::percent(accuracy = 1)

cod_o_first_blood_win_pct <- cod_rounds |> 
  filter(!is.na(earned_fb)) |> 
  filter(earned_fb) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop) |> 
  scales::percent(accuracy = 1)
```

@@

cod_heatmap_seq_labeller <- function(.df, .label, .num) {
  sprintf(
    '%s\n(%s)',
    scales::percent(.df[[.label]], accuracy = 1), 
    scales::comma(.df$n)
  )
}

o_round_win_text_layer <- function(
    ..., 
    .df,
    .threshold,
    .labeller,
    .label = 'win_round_prop',
    .num = 'win_round',
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- blackish_background
  } else {
    op <- `>=`
    .color <- 'white'
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = .label,
      .num = .num,
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller,
      .size = 11 / .pt
    )
  )
}

cod_heatmap_div_labeller <- function(.df, .label, .num) {
  sprintf(
    '%+.1f\n(%s)', 
    100 * .df[[.label]], 
    scales::comma(.df$n)
  )
}

@@

@@

  round_win_prop_after_x_wins |> 
    group_by(n_rounds, ...) |> 
    mutate(
      total = sum(n),
      prop = n / total
    ) |> 
    ungroup() |> 
    filter(win_round) |> 
    select(n_rounds, ..., n, total, prop) |> 
    arrange(n_rounds, ...) |> 
    inner_join(
      probs_nx_k
    ) |> 
    nest(data = -c(n_rounds, ...)) |> 
    mutate(
      gt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
          broom::tidy() |>
          pull(p.value)
      ),
      lt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
          broom::tidy() |>
          pull(p.value)
      ),
      gt_is_signif = gt_p_value <= 0.05,
      lt_is_signif = lt_p_value <= 0.05,
      is_signif = case_when(
        gt_is_signif ~ 'Better',
        lt_is_signif ~ 'Worse',
        TRUE ~ 'Neither'
      )
    ) |> 
    unnest(data)
}

@@

cod_round_win_prop_after_x_wins_and_rounds <- tibble(win_streak = 2L:4L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_x_wins_and_rounds)
  ) |>
  unnest(data)
save_qs(cod_round_win_prop_after_x_wins_and_rounds)
```

@@

```{r}
load_qs('cod_round_win_prop_after_x_wins')
ggsci_orange <- extract_ggsci_mid_color('orange')
p_cod_round_win_prop_after_x_wins_y_rounds <- cod_round_win_prop_after_x_wins_y_rounds |> 
  mutate(
    is_signif = case_when(
      gt_is_signif ~ 'Better',
      lt_is_signif ~ 'Worse',
      TRUE ~ 'Neither'
    )
  ) |> 
  # filter(win_streak %in% c(3, 4)) |> 
  # filter(n >= 20) |> 
  ggplot() +
  geom_tile(
    color = blackish_background,
    height = 0.8,
    aes(
      fill = is_signif,
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  geom_richtext(
    fill = NA_character_,
    label.color = NA_character_,
    family = font,
    color = blackish_background,
    size = 11 / .pt,
    fontface = 'bold',
    aes(
      label = sprintf(
        '%s %s <span style="color:white">%s</span><br/>(%s)',
        scales::percent(prop, accuracy = 1), 
        case_when(
          round(prop, 1) == round(expected_poststreak_p, 1) ~ '=',
          prop >= expected_poststreak_p ~ '>=', 
          TRUE ~ '<'
        ),
        scales::percent(expected_poststreak_p, accuracy = 1),
        scales::comma(n)
      ),
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  guides(
    fill = guide_legend(
      'Significantly better/worse?'
    )
  ) +
  scale_x_continuous(
    labels = 4:11,
    breaks = seq(4.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  scale_fill_manual(
    values = c(ggsci_cyan, ggsci_grey, ggsci_orange),
    labels = c('Better', 'Neither', 'Worse')
  ) +
  theme(
    legend.position = 'top',
    legend.text = element_text(color = 'white', size = 12),
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Post win streak round win %',
    x = 'Round',
    y = '# of rounds played in series'
  ) +
  facet_wrap(~win_streak)
p_cod_round_win_prop_after_x_wins_y_rounds
```

>>>>

cod_o_win_prop_const <- cod_rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop)
cod_o_win_pct <- scales::percent(cod_o_win_prop_const, accuracy = 0.1)

cod_plant_pct <- cod_rounds |>
  filter(is_offense) |> 
  count(makes_plant = !is.na(plant)) |> 
  mutate(prop = n / sum(n)) |> 
  filter(makes_plant) |> 
  pull(prop) |> 
  scales::percent(accuracy = 0.1)

cod_o_plant_and_win_pct <- cod_rounds |> 
  filter(is_offense, !is.na(plant)) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop) |> 
  scales::percent(accuracy = 0.1)

cod_o_first_blood_win_pct <- cod_rounds |> 
  filter(!is.na(earned_fb)) |> 
  filter(earned_fb) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop) |> 
  scales::percent(accuracy = 0.1)
```

@@

cod_heatmap_seq_labeller <- function(.df, .label, .num) {
  sprintf(
    '%s\n(%s)',
    scales::percent(.df[[.label]], accuracy = 0.1), 
    scales::comma(.df$n)
  )
}

o_round_win_text_layer <- function(
    ..., 
    .df,
    .threshold,
    .labeller,
    .label = 'win_round_prop',
    .num = 'win_round',
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- blackish_background
  } else {
    op <- `>=`
    .color <- 'white'
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = .label,
      .num = .num,
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller,
      .size = 11 / .pt
    )
  )
}
o_series_win_text_layer <- function(
    ..., 
    .df,
    .threshold,
    .labeller, 
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- blackish_background
  } else {
    op <- `>=`
    .color <- 'white'
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = 'win_series_prop',
      .num = 'win_series',
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller,
      .size = 9 / .pt
    )
  )
}
cod_heatmap_div_labeller <- function(.df, .label, .num) {
  sprintf(
    '%+.1f\n(%s)', 
    100 * .df[[.label]], 
    scales::comma(.df$n)
  )
}

@@

o_series_win_over_expected_text_layer <- function(
    ..., 
    .df,
    .threshold,
    .labeller, 
    .emphasize
) {
  if(.emphasize == 'low') {
    op <- `<`
    .color <- blackish_background
  } else {
    op <- `>=`
    .color <- 'white'
  }
  list(
    ...,
    heatmap_text_layer(
      .df = .df,
      .op = op,
      .label = 'diff_win_series_prop',
      .num = NULL,
      .color = .color,
      .threshold = .threshold,
      .labeller = .labeller,
      .size = 9 / .pt
    )
  )
}

@@

  suppressMessages(
  round_win_prop_after_x_wins_w_probs <- round_win_prop_after_x_wins |> 
    group_by(n_rounds, ...) |> 
    mutate(
      total = sum(n),
      prop = n / total
    ) |> 
    ungroup() |> 
    filter(win_round) |> 
    select(n_rounds, ..., n, total, prop) |> 
    arrange(n_rounds, ...) |> 
    inner_join(
      probs_nx_k
    )
  )

  round_win_prop_after_x_wins_w_probs |> 
    nest(data = -c(n_rounds, ...)) |> 
    mutate(
      gt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
          broom::tidy() |>
          pull(p.value)
      ),
      lt_p_value = map_dbl(
        data, 
        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
          broom::tidy() |>
          pull(p.value)
      ),
      gt_is_signif = gt_p_value <= 0.05,
      lt_is_signif = lt_p_value <= 0.05,
      is_signif = case_when(
        gt_is_signif ~ 'Better',
        lt_is_signif ~ 'Worse',
        TRUE ~ 'Neither'
      )
    ) |> 
    unnest(data)
}

@@

cod_round_win_prop_after_x_wins_y_rounds <- tibble(win_streak = 2L:4L) |>
  mutate(
    data = map(win_streak, summarize_cod_win_prop_after_x_wins_y_rounds)
  ) |>
  unnest(data)
save_qs(cod_round_win_prop_after_x_wins_y_rounds)
```

@@

```{r}
load_qs('cod_round_win_prop_after_x_wins_y_rounds')
ggsci_orange <- extract_ggsci_mid_color('orange')
p_cod_round_win_prop_after_x_wins_y_rounds <- cod_round_win_prop_after_x_wins_y_rounds |> 
  mutate(
    is_signif = case_when(
      gt_is_signif ~ 'Better',
      lt_is_signif ~ 'Worse',
      TRUE ~ 'Neither'
    )
  ) |> 
  # filter(win_streak %in% c(3, 4)) |> 
  # filter(n >= 20) |> 
  ggplot() +
  geom_tile(
    color = blackish_background,
    height = 0.8,
    aes(
      fill = is_signif,
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  geom_richtext(
    fill = NA_character_,
    label.color = NA_character_,
    family = font,
    color = blackish_background,
    size = 11 / .pt,
    fontface = 'bold',
    aes(
      label = sprintf(
        '%s %s <span style="color:white">%s</span><br/>(%s)',
        scales::percent(prop, accuracy = 1), 
        case_when(
          round(prop, 1) == round(expected_poststreak_p, 1) ~ '=',
          prop >= expected_poststreak_p ~ '>=', 
          TRUE ~ '<'
        ),
        scales::percent(expected_poststreak_p, accuracy = 1),
        scales::comma(n)
      ),
      x = round + 0.5, 
      y = n_rounds + 0.5
    )
  ) +
  guides(
    fill = guide_legend(
      'Significantly better/worse?'
    )
  ) +
  scale_x_continuous(
    labels = 4:11,
    breaks = seq(4.5, 11.5, by = 1),
    expand = c(0, 0.5)
  ) +
  scale_y_continuous(
    labels = 7:11,
    breaks = seq(7.5, 11.5, by = 1),
    expand = c(0, 0)
  ) +
  scale_fill_manual(
    values = c(ggsci_cyan, ggsci_grey, ggsci_orange),
    labels = c('Better', 'Neither', 'Worse')
  ) +
  theme(
    legend.position = 'top',
    legend.text = element_text(color = 'white', size = 12),
    panel.grid.major = element_blank(),
    axis.title = element_text(hjust = 0.5),
    plot.title = ggtext::element_markdown(hjust = 0.5),
    axis.text = element_text(size = 16, face = 'bold')
  ) +
  common_cod_labs() +
  labs(
    title = 'Post win streak round win %',
    x = 'Round',
    y = '# of rounds played in series'
  ) +
  facet_wrap(~win_streak)
p_cod_round_win_prop_after_x_wins_y_rounds
```
